% Owner: OpenAI Codex. Scope: T1 expressed affect.
% Signed: OpenAI Codex - 2026-07-19 (updated after Hanyang mocap and deception audits)
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{xurl}
\renewcommand{\texttt}[1]{\url{#1}}
\title{MARY T1 Expressed Affect: Artifact Ledger}
\author{BrainVI}
\date{2026-07-19}
\begin{document}
\maketitle

\section*{Scope}
T1 is displayed affect: face and body signals present in the stimulus.
Induced affect, physiology, BOLD, CASE, and viewer-state targets are out of
scope.

\section*{Established face transfer}
The current reported transfer cells and protocol are in
\texttt{EXPRESSED-AFFECT-gold-transfer-results.md}. Pearson correlation is
primary and CCC is secondary.

The locked AFEW-VA identity/group-CV result is recorded in
\texttt{results/expressed_t1/expressed_id_t1.json}. Across five group
folds, the commercial routed tier reaches mean Pearson $r=.643/.594$ for
valence/arousal, with no output collapse and 10,000-draw matched nulls per
fold. This is an in-domain identity/group robustness result, not LODO.

\section*{MPIIEmo research gate}
The acquisition, license, ceiling, and actor-ownership protocol are in
\texttt{T1-EXPRESSED-DATASET-LEDGER.md}. The recovered 448-trace ridge floor
is negative in both disjoint evaluations: pair-held-out valence/arousal
Pearson $r=-.068/-.112$, and scenario-held-out $r=-.357/-.311$.
Matched circular-null $p$ values are $(.9997,.4969)$ and $(.9356,.1192)$;
neither split collapsed. This is a diagnostic failure floor, not a promoted
training result; the full JSON remains authoritative.

\section*{Pillar 3}
The body adapter is
\texttt{experiments/scaling-sota-head/freemocap_kinematics.py}. It reports
kinematics and quality diagnostics. The complete HEROES categorical smoke
benchmark has 256 reconciled native-resolution outputs. The frozen ridge
floor (temporal mean+SD pooling, source-only standardization) gives
actor-held-out balanced accuracy/macro-F1 $=.441/.442$, scenario $=.367/.365$,
and camera $=.313/.312$. The matched 10,000-draw within-group fixed-prediction
label null gives $p=.0001$ for actor and scenario and $p=1.0$ for camera. This
is not a continuous BoLD result; the authoritative JSON is
\texttt{results/heroes_t1/heroes_body_t1.json} and the durable archive is
\texttt{s3://Neuropeer/orcle/research/scaling_sota_head/heroes_t1/freemocap_20260719/}.

The open-license MEED left-view benchmark is a separate categorical body
result: 1,386 recordings from 22 actors and seven classes. Actor-held-out
normalized 2-D pose/velocity ridge gives balanced accuracy/macro-F1
$.539/.514$ across three seeds. Its authoritative JSON is
\texttt{results/expressed_t1/meed_body_t1_20260719.json} (SHA-256
\texttt{4a31422b5f07c1154140af80e926dc971f7b1ac84700c1ff4400133cfc626673}).
A fixed higher-order ablation adding acceleration, jerk, and expansiveness
falls to $.533/.514$, so the added dynamics are retained as negative evidence
under \texttt{meed_body_t1_higher_order_20260719.json} (SHA-256
\texttt{0f58ddd168676041270fe4e14de836a62df81009f85eeb5c46b0cc3b61e433c9}).

The Hanyang Emotional body motion control corpus adds 4,060 five-second,
19-joint 3-D trials from 29 participants and seven instructed emotions. The
participant-held-out ridge floor reaches balanced accuracy/macro-F1
$.447/.443$ on intended labels and $.468/.476$ on observer-majority labels.
The 13-rater mean per-motion majority agreement is $.635$; both model targets
use 10,000 matched within-participant permutations. This is elicited,
research-only mocap control evidence, not in-the-wild BoLD transfer. The
authoritative artifact is
\texttt{results/expressed_t1/emotional_body_motion_t1_20260719.json}
(SHA-256 \texttt{a8bc6f899ab1d53aca04517e78ef07d0206a4ef25547c98fcb2f46e15364e7a1}).

The locked cross-representation stress test uses 18 common scalar kinematic
features and the same seven labels. Hanyang$\rightarrow$MEED macro-F1 is
$.083$ and MEED$\rightarrow$Hanyang is $.046$, below the seven-class reference
$.143$; both predictions collapse to three labels. This is negative transfer
evidence, traced to
\texttt{results/expressed_t1/body_motion_transfer_t1_20260719.json}
(SHA-256 \texttt{886664caf8a2cfb21aeb75c974fc6ac88a867fc0b414b73ae11de3fcae6c0bf7}).

The verified MPIIEmo continuous-body floor is separate from these categorical
benchmarks. A normalized COCO17 2-D pose proxy with portrait identity gating
reaches pair-held-out Pearson $r=-.038/.143$ and scenario-held-out
$r=-.026/.085$ for valence/arousal. Matched circular-null $p$ values are
$(.3108,.0028)$ and $(.6793,.0005)$. The run produced 295 valid traces from
448 actor-owned videos; 153 unmatched videos remain in the manifests. This is
research-only pose-proxy evidence, not a FreeMoCap or commercial
full-coverage claim. The authoritative artifact is
\texttt{results/expressed_t1/mpiiemo_body_t1_20260719.json} (SHA-256
\texttt{ee8d884bfbb2798eef99ff496ff6c4afab9342b327d7fc9ed6d009e0f98825ab}).
Each cell includes 5,000 whole-group bootstrap draws in addition to the
10,000 matched nulls.

After both streams were independently evaluated, a matched face/body ridge
ablation used the same 542 paired rows. Pair-held-out valence/arousal Pearson
$r=.020/.129$ and scenario-held-out $r=-.033/.130$; matched-null $p$ values
are $(.828,.240)$ and $(.769,.0255)$. The scenario arousal cell does not
replicate in the pair split, so fusion is retained as limited negative evidence
and is not promoted. Its authoritative JSON is
\texttt{results/expressed_t1/mpiiemo_fusion_t1_20260719.json}.

\section*{Temporal head comparison}
The complete three-seed temporal comparison is traced in
\texttt{T1-TEMPORAL-HEAD-RESULTS.md}. AFEW-VA$\rightarrow$VEATIC GRU heads
remain modestly positive (best mean valence $r=.219$, arousal $r=.223$),
but VEATIC$\rightarrow$AFEW-VA is negative on valence for every head (best
mean $r=-.096$) and near-null on arousal. TCN+LSTM does not improve transfer
robustness; the representation/domain shift remains the limiting failure.

\section*{Video-stream modality ablation}
On the AFEW-VA$\rightarrow$VEATIC transfer, source-only video-stream ablation
gives mean Pearson valence/arousal $=.121/.221$ for SlowFast-only,
$.346/.316$ for VL-only, and $.351/.342$ for fused video (three seeds each).
The 10,000-draw target-clip circular null is recorded per seed in
\texttt{results/expressed_t1/modality_ablation_t1.json}; audio and text are
not ablated because they are absent from the AFEW source pool.

\section*{Artifact traceability}
Every future headline number must cite its result JSON, prediction array,
manifest, checksum, and evaluation command. The microexpression disposition is
recorded in \texttt{T1-MICROEXPRESSION-GATE.md}: acquisition and rights are
pending, with no model claim. The deception disposition is recorded in
\texttt{T1-DECEPTION-CUE-GATE.md}. The T1-only runtime/package boundary is
frozen in \texttt{experiments/scaling-sota-head/production/t1_expressed_manifest.json};
its body branch is research-only and T2/T3 are excluded.

\section*{Package readiness correction}
The available research transfer checkpoints are preserved in
\texttt{research_transfer_checkpoint_manifest_t1_20260719.json} (12 files,
SHA-256 \texttt{f35c6cad863afb2b6a0aa3cd58ccba51ba35e726969e2642342bd43b4db7e44d})
and copied to the expressed-affect B2 checkpoint prefix. They are branch-level
research transfer artifacts, not the combined routed inference artifact. The
combined six-seed commercial-code package is separately inventoried under the
legacy \texttt{routed_expressed_va/packaged/} prefix. The commercial package
is therefore \textbf{not frozen for distribution}: AFEW-VA/VEATIC training
rights remain unresolved.
\texttt{T1-DECEPTION-CUE-GATE.md}: production lie detection is rejected at the
current evidence gate, with no trained result. The official Michigan archive
is locally intact (121 clips, 61 deceptive/60 truthful), but its files expose
no clip-to-speaker mapping for the 56 speakers reported in the paper and do
not clear redistribution. Its acquisition audit is
\texttt{results/expressed_t1/reallife_deception_acquisition_audit_20260719.json}
(SHA-256 \texttt{5566445343c2569849171691ea7a45e970522ddd34f3683b03fdc5b8700a09a6});
no model or calibration claim is made. The HEROES body numbers above
are traced to
\texttt{results/heroes_t1/heroes_body_t1.json} (SHA-256
\texttt{92bc01b7a482292911093a0548dd291495f4563bee46a108e0ba1d009817a1c2})
and the 256-entry checksum manifest
\texttt{results/heroes_t1/artifact_checksums.sha256}.
The identity result hash is
\texttt{867902af53f1e1a18a90a9532671590650806fca3e213ae69f9e3f628e8c6351}.
\end{document}
